\documentclass[11pt,a4paper]{article}

%----------------------------------------------------------------------------------------
% PACKAGES
% Template style adapted from the MBZUAI Resume Template by MBZUAI Library
% License: Creative Commons CC BY 4.0
%----------------------------------------------------------------------------------------
\usepackage[left=0.8in,top=0.8in,right=0.8in,bottom=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

%----------------------------------------------------------------------------------------
% COLORS & STYLES
%----------------------------------------------------------------------------------------
\definecolor{titleblue}{HTML}{00199e}
\definecolor{subtitleblue}{HTML}{2ec1e0}
\definecolor{darktext}{HTML}{222222}

\color{darktext}
\linespread{0.9}
\setlength{\parskip}{0.1em}
\titleformat{\section}{\Large\bfseries\color{titleblue}}{}{0em}{}
\titlespacing*{\section}{0pt}{0.7em}{0.15em}

\newcommand{\blueitem}[1]{\textcolor{subtitleblue}{\textbf{#1}}}

\setlist[itemize]{label=\textbullet, leftmargin=*, noitemsep, topsep=0pt, parsep=0pt}

%----------------------------------------------------------------------------------------
% DOCUMENT CONTENT
%----------------------------------------------------------------------------------------
\begin{document}

%--- HEADER ---
{\Huge \textbf{\textcolor{titleblue}{Pengyi Chen}}} \vspace{0.2em}

Shanghai, China \\
Email: \href{mailto:lotus_thrash@sjtu.edu.cn}{lotus\_thrash@sjtu.edu.cn} \\
Gmail: \href{mailto:lotusthrash@gmail.com}{lotusthrash@gmail.com} \\
QQ Mail: \href{mailto:571881662@qq.com}{571881662@qq.com} \\
GitHub: \href{https://github.com/ThrasHl}{github.com/ThrasHl}

\vspace{0.4em}

%--- EDUCATION ---
\section*{Education}
\blueitem{Sep. 2023 -- Present: B.Eng. in Artificial Intelligence} \\
\textit{Shanghai Jiao Tong University, Shanghai, China}

\vspace{0.2em}
Average GPA: 3.6/4.3 \\
Rank: 63/98

%--- HONORS ---
\section*{Honors}
\blueitem{2023 -- 2024: \href{https://zhiyuan.sjtu.edu.cn/}{Zhiyuan Honors Program}} \\
Selected honors program at Shanghai Jiao Tong University.

\vspace{0.2em}
\blueitem{2023 -- 2024: Zhiyuan Honors Scholarship} \\
Scholarship recognition during undergraduate study.

%--- INTERNSHIP ---
\section*{Internship}
\blueitem{2025 -- Present: Research Intern} \\
\textit{\href{https://cvl.sjtu.edu.cn/}{SJTU CVL Lab}}
\begin{itemize}
    \item Explored computer vision fundamentals through research practice.
    \item Participated in research on wafer edge detection and defect detection.
    \item Studied vision-based inspection scenarios related to wafer manufacturing data.
\end{itemize}

%--- RESEARCH INTERESTS ---
\section*{Research Interests}
\blueitem{Current Focus:} Computer Vision \\
\blueitem{Broader Interests:} Agents, Large Language Models, and interdisciplinary AI applications.

%--- SKILLS ---
\section*{Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, C++
    \item \textbf{Tools:} Git, Jupyter, LaTeX
    \item \textbf{Agents:} Codex, Trae
    \item \textbf{Languages:} English (Fluent), Chinese (Native)
\end{itemize}

%--- PROJECTS ---
\section*{Projects}

\end{document}
